%-------------------------
% Resume in Latex
% Author : Madhav Sachdeva
% License : MIT
%------------------------

\documentclass[letterpaper,10pt]{article}

\usepackage{latexsym}
\usepackage[empty]{fullpage}
\usepackage{titlesec}
\usepackage{marvosym}
\usepackage[usenames,dvipsnames]{color}
\usepackage{verbatim}
\usepackage{enumitem}
\usepackage[hidelinks]{hyperref}
\usepackage{fancyhdr}
\usepackage[english]{babel}
\usepackage{tabularx}
\usepackage{fontawesome5}

% Ensure that generate pdf is machine readable/ATS parsable
\ifdefined\pdfgentounicode
  \input{glyphtounicode}
  \pdfgentounicode=1
\fi

\usepackage[scale=0.90,lf]{FiraMono}

% light-grey
\definecolor{light-grey}{gray}{0.83}
\definecolor{dark-grey}{gray}{0.3}
\definecolor{text-grey}{gray}{.08}

\usepackage[T1]{fontenc}
\usepackage{tgheros}
\renewcommand*\familydefault{\sfdefault} 

\pagestyle{fancy}
\fancyhf{} % clear all header and footer fields
\fancyfoot{}
\renewcommand{\headrulewidth}{0pt}
\renewcommand{\footrulewidth}{0pt}

% Adjust margins
\addtolength{\oddsidemargin}{-0.5in}
\addtolength{\evensidemargin}{0in}
\addtolength{\textwidth}{1in}
\addtolength{\topmargin}{-.5in}
\addtolength{\textheight}{1.0in}

\urlstyle{same}
\raggedbottom
\raggedright
\setlength{\tabcolsep}{0in}

% sans serif sections
\titleformat {\section}{
    \bfseries \vspace{2pt} \raggedright \large % header section
}{}{0em}{}[\color{light-grey} {\titlerule[2pt]} \vspace{-4pt}]

% Custom commands
\newcommand{\resumeItem}[1]{
  \item\small{
    {#1 \vspace{-1pt}}
  }
}

\newcommand{\resumeSubheading}[4]{
  \vspace{-1pt}\item
    \begin{tabular*}{\textwidth}[t]{l@{\extracolsep{\fill}}r}
      \textbf{#1} & {\color{dark-grey}\small #2}\vspace{1pt}\\ 
      \textit{#3} & {\color{dark-grey} \small #4}\\ 
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeProjectHeading}[2]{
    \item
    \begin{tabular*}{\textwidth}{l@{\extracolsep{\fill}}r}
      #1 & {\color{dark-grey}\small #2} \\
    \end{tabular*}\vspace{-4pt}
}

\newcommand{\resumeSubHeadingListStart}{\begin{itemize}[leftmargin=0in, label={}]}
\newcommand{\resumeSubHeadingListEnd}{\end{itemize}}
\newcommand{\resumeItemListStart}{\begin{itemize}}
\newcommand{\resumeItemListEnd}{\end{itemize}\vspace{0pt}}

\AtBeginDocument{\fontsize{10.8pt}{13pt}\selectfont}

\color{text-grey}

%-------------------------------------------
%%%%%%  RESUME STARTS HERE  %%%%%%%%%%%%%%%%%%%%%%%%%%%%

\begin{document}

%----------HEADING----------
\begin{center}
    \textbf{\Huge Madhav Sachdeva} \\ \vspace{5pt}
    \small \texttt{+91 97795 33777} \hspace{1pt} $|$
    \hspace{1pt} \href{mailto:madhavsachdeva613@gmail.com}{\texttt{madhavsachdeva613@gmail.com}} \hspace{1pt} $|$ 
    \hspace{1pt} \href{https://www.linkedin.com/in/madhav-sachdeva-75aa22360/}{\texttt{linkedin.com/in/madhav-sachdeva-75aa22360}} \\ \vspace{2pt}
    \small \href{https://github.com/MadhavS123-cloud}{\texttt{github.com/MadhavS123-cloud}} \hspace{1pt} $|$
    \hspace{1pt} \href{https://leetcode.com/u/4LxMIZA1cP/}{\texttt{leetcode.com/madhav}} \hspace{1pt} $|$
    \hspace{1pt} \href{https://www.codechef.com/users/madhavsachdeva}{\texttt{codechef.com/madhav}}
    \\ \vspace{-3pt}
\end{center}

%-----------EDUCATION-----------
\section{EDUCATION}
  \resumeSubHeadingListStart
    \resumeSubheading
      {Bachelor of Technology in Computer Science}{2025 -- 2029 (Expected)}
      {First Year Student}{India}
      \resumeItemListStart
        \resumeItem{\textbf{Relevant Coursework}: Data Structures and Algorithms, Object-Oriented Programming, Discrete Mathematics}
        \resumeItem{Passionately learning and applying core CS concepts in personal and academic projects}
      \resumeItemListEnd
  \resumeSubHeadingListEnd

%-----------PROJECTS-----------
\section{PROJECTS}
    \resumeSubHeadingListStart

        \resumeProjectHeading
          {\href{https://skill-match-ai.onrender.com/}{\textbf{Skill Match AI}} $|$ \href{https://github.com/MadhavS123-cloud/Skill-Match-AI}{GitHub}}{Feb. 2026}
          \resumeItemListStart
            \resumeItem{Architected an AI-powered resume parsing and ATS score calculation system using \textbf{Python} and \textbf{FastAPI}}
            \resumeItem{Integrated \textbf{PostgreSQL} for persistent storage of candidate profiles and leveraged \textbf{Render} for automated cloud deployment.}
            \resumeItem{Implemented a Hiring Manager Rejection Simulator using \textbf{Large Language Models}, increasing evaluation efficiency by \textbf{55\%} for \textbf{200+} analyzed resumes.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\href{https://eris-emergency-response-intelligent.vercel.app/}{\textbf{ERIS — Emergency Response System}} $|$ \href{https://github.com/MadhavS123-cloud/ERIS-Emergency-Response-Intelligent-System-}{GitHub}}{Mar. 2026}
          \resumeItemListStart
            \resumeItem{Architected a modular dispatch platform using \textbf{Node.js}, \textbf{Express.js}, and \textbf{PostgreSQL} for real-time telemetry and dispatching.}
            \resumeItem{Developed a scalable engine with \textbf{Redis} for asynchronous dispatch and deployed the stack using \textbf{Docker} for high availability.}
            \resumeItem{Optimized emergency routing efficiency by \textbf{25\%} and reduced dispatch response time by \textbf{40\%} through dynamic capacity telemetry.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\href{https://financetracker-lemon.vercel.app/}{\textbf{Finora — Finance Tracker}} $|$ \href{https://github.com/MadhavS123-cloud/finance_tracker}{GitHub}}{Jan. 2026}
          \resumeItemListStart
            \resumeItem{Developed a comprehensive finance dashboard using \textbf{React.js}, \textbf{Node.js}, and \textbf{PostgreSQL} with role-based access control.}
            \resumeItem{Implemented interactive visualizations using \textbf{Recharts} and optimized data fetching with \textbf{RESTful} best practices.}
            \resumeItem{Achieved a \textbf{95\%} performance score on Core Web Vitals and a \textbf{92\%} user satisfaction rating across \textbf{75+} active users.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\href{https://resilient-paletas-3875fc.netlify.app/}{\textbf{Personal Portfolio Website}}}{2025}
          \resumeItemListStart
            \resumeItem{Developed a highly interactive, responsive personal portfolio to showcase AI/ML projects and full-stack expertise}
            \resumeItem{Implemented high-performance features like glassmorphism and smooth scroll with \textbf{GSAP} animations}
            \resumeItem{Achieved a \textbf{99/100} Lighthouse accessibility score and reduced time-to-interactive by \textbf{30\%} for over \textbf{500+} unique visitors.}
          \resumeItemListEnd

        \resumeProjectHeading
          {\textbf{Ecommerce-Vibe}}{Mar. 2026}
          \resumeItemListStart
            \resumeItem{Developed a full-stack e-commerce platform using \textbf{React.js}, \textbf{Node.js}, \textbf{Express.js}, and \textbf{PostgreSQL} with \textbf{JWT Authentication}.}
            \resumeItem{Implemented complex state management and \textbf{RESTful APIs} for seamless product management and persistent shopping cart state.}
            \resumeItem{Leveraged \textbf{Framer Motion} and \textbf{Tailwind CSS} for micro-animations, improving user engagement by \textbf{30\%} in beta testing.}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-----------SKILLS-----------
\section{SKILLS}
 \begin{itemize}[leftmargin=0in, label={}]
    \small{\item{
      \textbf{Languages} {: JavaScript (Node.js, Express.js, React.js), Python (FastAPI, Flask), SQL (PostgreSQL), HTML/CSS, NoSQL}\vspace{2pt} \\
      \textbf{Tools/Frameworks} {: RESTful APIs, Docker, Redis, Git, GitHub, JWT, Tailwind CSS, Framer Motion, GSAP}}
 \end{itemize}

%-----------ACHIEVEMENTS-----------
\section{ACHIEVEMENTS}
    \resumeSubHeadingListStart
        \resumeProjectHeading
          {\textbf{Competitive Programming Milestone}}{}
          \resumeItemListStart
            \resumeItem{Earned the \textbf{Diamond Badge} for solving over \textbf{1000+ problems} across LeetCode and CodeChef}
            \resumeItem{Demonstrated strong problem-solving skills and consistency in Data Structures and Algorithms (DSA)}
          \resumeItemListEnd
    \resumeSubHeadingListEnd

%-------------------------------------------
\end{document}
